OptiFit: an improved method for fitting amplicon sequences to existing OTUs

### 2021-10-30 paper/paper.Rmd
Manually set fig2 dimensions to remove gray bar
dot didn't output it as exactly 6x4, so Rmd was adding a gray bar to make up for it.
Corrected it by adding in the actual dimensions of the tiff file.
Use imagemagick to fix gray bar in workflow figure

```{r workflow, fig.dim=figs('workflow','dim'), fig.cap=figs('workflow','cap')}
figs('workflow', 'path') %>%
  tiff::readTIFF() %>%
  grid::grid.raster()
```

>>>>

```{r workflow, fig.dim=figs('workflow', 'dim'), fig.cap=figs('workflow','cap')}
figs('workflow', 'path') %>%
  tiff::readTIFF() %>%
  grid::grid.raster()
```
